### 2015-02-21 zoldatoff/tex/pattern discovery/lecture05.tex
Конспект лекций 2-й недели курса Pattern Discovery
Добавлены лекции 6.4 - 6.8

Redundancy filtering: some rules may be redundant due to <<ancestor\footnote{Ancestor -- предок}>> relationships between items. A rule is \textbf{redundant} if:
\begin{itemize}
\item its support is close to the <<expected>> value, according to its <<ancestor>> rule
\item it has a similar confidence as its <<ancestor>>.
\end{itemize}\\

@@

\textbf{$\delta$-clustering}. For each pattern P, find all patterns which can be expressed by P and whose distance to P is within $\delta$ ($\delta$-cover). All patterns in the cluster can be represented by P = compressed patterns.\\

@@

Use \textbf{MMS (Maximal Marginal Significance)} for measuring the combined significance of a pattern set: Xin et al., Extracting Redundancy\footnote{Redundancy - избыточность}-Aware Top-K Patterns, KDD’06.

@@

\subsubsection{Robustness of Colossal Patterns}
For a frequent pattern $\alpha$, a subpattern $\beta$ is a $\tau$-core pattern of $\alpha$ if $\beta$ shares a similar support set with $\alpha$, i.e., 
\begin{equation*}
\frac{\abs{D_\alpha}}{\abs{D_\beta}} \geqslant \tau, 0 < \tau \leqslant 1, 
\end{equation*}
where \tau is called the \textbf{core ratio}.\\

\textbf{$(d, \tau)$-robustness}\footnote{Robustness - прочность}: a pattern $\alpha$ is $(d, \tau)$-robust if d is the maximum number of items that can be removed from $\alpha$ for the resulting pattern to remain a $\tau$-core pattern of $\alpha$. For a $(d, \tau)$-robust pattern $\alpha$, it has $\Omega (2^d)$ core patterns.\\

>>>>

Redundancy\footnote{Redundancy - избыточность} filtering: some rules may be redundant due to <<ancestor>>\footnote{Ancestor -- предок} relationships between items. A rule is \textbf{redundant} if:
\begin{itemize}
\item its support is close to the <<expected>> value, according to its <<ancestor>> rule
\item it has a similar confidence as its <<ancestor>>.
\end{itemize}\\

@@

\textbf{$\mathbf{\delta}$-clustering}. For each pattern P, find all patterns which can be expressed by P and whose distance to P is within $\delta$ ($\delta$-cover). All patterns in the cluster can be represented by P = compressed patterns.\\

@@

Use \textbf{MMS (Maximal Marginal Significance)} for measuring the combined significance of a pattern set: Xin et al., Extracting Redundancy-Aware Top-K Patterns, KDD’06.

@@

\subsubsection{Robustness of Colossal Patterns}
For a frequent pattern $\alpha$, a subpattern $\beta$ is a $\tau$-core pattern of $\alpha$ if $\beta$ shares a similar support set with $\alpha$, i.e., 
\begin{equation*}
\frac{\abs{D_\alpha}}{\abs{D_\beta}} \geqslant \tau, 0 < \tau \leqslant 1, 
\end{equation*}
where $\tau$ is called the \textbf{core ratio}.\\

\textbf{$\mathbf{(d, \tau)}$-robustness}\footnote{Robustness - прочность}: a pattern $\alpha$ is $(d, \tau)$-robust if d is the maximum number of items that can be removed from $\alpha$ for the resulting pattern to remain a $\tau$-core pattern of $\alpha$. For a $(d, \tau)$-robust pattern $\alpha$, it has $\Omega (2^d)$ core patterns.\\

### 2015-02-21 zoldatoff/tex/pattern discovery/lecture06.tex
Конспект лекций 2-й недели курса Pattern Discovery
Добавлены лекции 6.4 - 6.8

Constraint c is \textbf{anti-monotone}: if an itemset S violates constraint c, so does any of its superset. That is, mining on itemset S can be terminated. For example, constraint $\sup(S) \geqslant \sigma$ is anti-monotone.

>>>>

Anti-monotonic constraints have more pruning power than monotonic constraints.

\subsubsection{Pattern space pruning constraints}
Constraint c is \textbf{anti-monotone}: if an itemset S violates constraint \textbf{c}, so does any of its superset. That is, mining on itemset S can be terminated. For example, constraint $\sup(S) \geqslant \sigma$ is anti-monotone.\\

A constraint c is \textbf{monotone}: if an itemset S satisfies the constraint \textbf{c}, so does any of its superset. That is, we do not need to check \textbf{c} in subsequent mining. For example, constraints $\sum(S.price) \geqslant v$ or $\min(S.price) \leqslant v$ are monotone.

\subsubsection{Data space pruning constraints}
A constraint \textbf{c} is \textbf{data anti-monotone}: if a data entry \textbf{t} cannot satisfy a pattern \textbf{p} under constraint \textbf{c}, \textbf{t} cannot satisfy \textbf{p}’s superset either. That's why, data entry \textbf{t} can be pruned.\\

\textbf{Succinctness}: if the constraint \textbf{c} can be enforced by directly manipulating the data.\\

\textbf{Convertible constraints}: convert tough\footnote{Tough - жесткий} constraints into (anti-)monotone by proper ordering of items in transactions. For example, ordering items in value-descending order makes the constraint $avg(S.profit) > 20$ anti-monotone \textit{if the patterns grow in the right order}.

%--
\subsection{Recommended Readings}
\begin{itemize}
\item R. Srikant, Q. Vu, and R. Agrawal, <<Mining association rules with item constraints>>, KDD'97
\item R. Ng, L.V.S. Lakshmanan, J. Han \& A. Pang, Exploratory mining and pruning optimizations of constrained association rules>>, SIGMOD’98
\item G. Grahne, L. Lakshmanan, and X. Wang, <<Efficient mining of constrained correlated sets>>, ICDE'00
\item J. Pei, J. Han, and L. V. S. Lakshmanan, <<Mining Frequent Itemsets with Convertible Constraints>>, ICDE'01
\item J. Pei, J. Han, and W. Wang, <<Mining Sequential Patterns with Constraints in Large Databases>>, CIKM'02
\item F. Bonchi, F. Giannotti, A. Mazzanti, and D. Pedreschi, <<ExAnte: Anticipated Data Reduction in Constrained Pattern Mining>>, PKDD'03
\item F. Zhu, X. Yan, J. Han, and P. S. Yu, <<gPrune: A Constraint Pushing Framework for Graph Pattern Mining>>, PAKDD'07
\end{itemize}
